INSEE_vaccination_COVID

### 2021-09-08 code/INSEE_vaccination_COVID.Rmd
update code and fix bugs

GEO_fact = GEO %>%
  filter(codgeo %in% c(GEO_gua$SIREN_EPCI, GEO_guy$SIREN_EPCI, GEO_mar$SIREN_EPCI, GEO_may$SIREN, GEO_reu$SIREN_EPCI)) %>%
  select(-c(latitude, longitude)) %>%
  plyr::rbind.fill(GEO %>%
                     filter(!(codgeo %in% c(GEO_gua$SIREN_EPCI, GEO_guy$SIREN_EPCI, GEO_mar$SIREN_EPCI, GEO_may$SIREN, GEO_reu$SIREN_EPCI)))) %>%
  select(codgeo, latitude, longitude, densite, taux_cumu_1_inj) %>%
  mutate(across(-c(codgeo, taux_cumu_1_inj), binarisation)) %>%
  mutate(taux_cumu_1_inj = binarisation(taux_cumu_1_inj, 0.25),
         taux_cumu_1_inj = as.factor(if_else(taux_cumu_1_inj == 1, 0, 1)))
```

@@

```{r}
GEO_OR = questionr::odds.ratio(GEO_fact$latitude, GEO_fact$taux_cumu_1_inj) %>%
  rbind(questionr::odds.ratio(GEO_fact$longitude, GEO_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(GEO_fact$densite, GEO_fact$taux_cumu_1_inj)) %>%
  as.data.frame() %>%
  bind_cols(Variable = colnames(GEO_fact)[2:4]) %>%
  select(Variable, OR, `2.5 %`, `97.5 %`, p)
rownames(GEO_OR) = NULL
write_csv2(GEO_OR, "data/GEO_OR.csv")
```

@@

```{r}
make_data_covid = function(wk){
  vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
    rename(codgeo = commune_residence) %>%
    select(codgeo, taux_cumu_1_inj) %>%
    mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))

@@

  GEO_OR_1107 = questionr::odds.ratio(GEO_1107$latitude, GEO_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(GEO_1107$longitude, GEO_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(GEO_1107$densite, GEO_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(GEO_1107)[2:4]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(GEO_OR) = NULL
  # write_csv2(GEO_OR, "data/GEO_OR.csv")

>>>>

GEO_OM$lat01 <- (GEO_OM$latitude - min(GEO_OM$latitude, na.rm = T)) / (max(GEO_OM$latitude, na.rm = T) - min(GEO_OM$latitude, na.rm = T))
GEO_OM$lon01 <- (GEO_OM$longitude - min(GEO_OM$longitude, na.rm = T)) / (max(GEO_OM$longitude, na.rm = T) - min(GEO_OM$longitude, na.rm = T))

GEO_OM = GEO_OM %>%
  mutate(`SO-NE` = lat01+lon01,
         `NO-SE` = lon01-lat01)

GEO_fact = GEO_OM %>%
  select(codgeo, latitude, longitude, densite, taux_cumu_1_inj) %>%
  mutate(across(-c(codgeo, taux_cumu_1_inj), binarisation)) %>%
  mutate(taux_cumu_1_inj = binarisation(taux_cumu_1_inj, 0.25),
         taux_cumu_1_inj = as.factor(if_else(taux_cumu_1_inj == 1, 0, 1)))
```

@@

```{r}
GEO_OR = questionr::odds.ratio(GEO_fact$latitude, GEO_fact$taux_cumu_1_inj) %>%
  rbind(questionr::odds.ratio(GEO_fact$longitude, GEO_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(GEO_fact$densite, GEO_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(GEO_fact$`SO-NE`, GEO_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(GEO_fact$`NO-SE`, GEO_fact$taux_cumu_1_inj)) %>%
  as.data.frame() %>%
  bind_cols(Variable = colnames(GEO_fact)[2:6]) %>%
  select(Variable, OR, `2.5 %`, `97.5 %`, p)
rownames(GEO_OR) = NULL
write_csv2(GEO_OR, "data/GEO_OR.csv")
```

@@

```{r}
make_data_covid = function(wk){

  if (wk/10 <1){
    wk = paste0("0", wk)
  }

  vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
    rename(codgeo = commune_residence) %>%
    select(codgeo, taux_cumu_1_inj) %>%
    mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))

@@

  GEO_OR_1107 = questionr::odds.ratio(GEO_1107$latitude, GEO_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(GEO_1107$longitude, GEO_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(GEO_1107$densite, GEO_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(GEO_fact$`SO-NE`, GEO_fact$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(GEO_fact$`NO-SE`, GEO_fact$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(GEO_1107)[2:6]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(GEO_OR) = NULL
  # write_csv2(GEO_OR, "data/GEO_OR.csv")
